Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-22 paper.tex
i.e. should use emph

The relative blade velocity $U_\mathrm{rel}$ was calculated by vector addition
of the free stream velocity and the opposite of the blade tangential velocity.
Note that this neglects any induction, i.e., slowing of the free stream by the
turbine forces, which would be present in a momentum/streamtube model. Since~the
goal of this approach was not to predict absolute performance, but rather to
gain insight into relative changes with $Re$, this method was deemed acceptable,
as it is extremely simple and fast to~compute.

>>>>

The relative blade velocity $U_\mathrm{rel}$ was calculated by vector addition
of the free stream velocity and the opposite of the blade tangential velocity.
Note that this neglects any induction, \emph{i.e.}, slowing of the free stream
by the turbine forces, which would be present in a momentum/streamtube model.
Since~the goal of this approach was not to predict absolute performance, but
rather to gain insight into relative changes with $Re$, this method was deemed
acceptable, as it is extremely simple and fast to~compute.
